---
title: "Bayes Modeling and Prediction for Movies"
output:
        html_document:
                toc: TRUE
editor_options: 
  chunk_output_type: console
---
## Part 0: Setup

### 0.1 Load packages

The libraries used in this study are `ggplot2`, `dplyr`, `statsr`, `BAS` and
`kableExtra`. Please ensure these libraries are installed to reproduce this paper.

```{r load-packages, message = FALSE, warnings = FALSE, comments = NA}
library(ggplot2); library(dplyr)
library(statsr); library(BAS); 
library(kableExtra)
```

### 0.2 Load data

```{r load-data}
load("data/movies.Rdata")

head(movies) %>%
        kable() %>%
        kable_styling("striped") %>%
        scroll_box(width = "100%")
```



* * *

## Part 1: Data


* * *

## Part 2: Data manipulation

NOTE: Insert code chunks as needed by clicking on the "Insert a new code chunk" 
button above. Make sure that your code is visible in the project you submit. 
Delete this note when before you submit your work.

* * *

## Part 3: Exploratory data analysis

NOTE: Insert code chunks as needed by clicking on the "Insert a new code chunk" 
button above. Make sure that your code is visible in the project you submit. 
Delete this note when before you submit your work.

* * *

## Part 4: Modeling

NOTE: Insert code chunks as needed by clicking on the "Insert a new code chunk" 
button above. Make sure that your code is visible in the project you submit. 
Delete this note when before you submit your work.

* * *

## Part 5: Prediction

NOTE: Insert code chunks as needed by clicking on the "Insert a new code chunk" 
button above. Make sure that your code is visible in the project you submit. 
Delete this note when before you submit your work.

* * *

## Part 6: Conclusion

